Predicted cardiovascular risk for US adults with diabetes, chronic kidney disease, and \u226565 years of age

### 2021-06-24 doc/JoH submission/reviewer_response/reviewer_response.Rmd

N_s1h_lowrisk_unwtd <- list(
  ovrl         = nrow(s1hyp_lowrisk),
  diab         = sum(s1hyp_lowrisk$diabetes == "yes"),
  ckd          = sum(s1hyp_lowrisk$ckd == "yes"),
  age_gt65     = sum(s1hyp_lowrisk$age_gt65 == "yes"),
  any          = sum(s1hyp_lowrisk$any_ckd_diab_age65 == "yes")
) %>%
  map_chr(table_value)

```

# Reviewer 1

__Reviewer's Summary__: Authors used the NHANES database to assess the prevalence of elevated 10-year predicted risk according to the ASCVD risk score in various groups of blood pressure. The paper is well-written and provides data supporting the recommendations made by the AHA/ACC Guidelines when to initiate antihypertensive medication.

@@

<br>

__Comment 3__ Results, It would be interesting to provide data on the number/characteristics of patients who would have received antihypertensive medication according to the ACC/AHA GL (stage 1 hypertension) but have an ASCVD risk score <10% (and would not be treated according to the ESC/ESH GL).

__Response__: We agree and have taken three steps in response:

_Step 1_: We computed the percentage of US adults with 10-year predicted ASCVD risk < 10% and with stage 1 hypertension who would be assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age ≥ 65 years. In the revised manuscript, we have included this information. Specifically, on page 9-10, we write "The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed." On page 11, we write "Overall, `r table_value(perc_assumed_highrisk)`% of those with stage 1 hypertension and without high ASCVD risk were assumed to have high ASCVD risk by the ACC/AHA BP guideline."

@@

__Response__: We are happy to answer this question. All NHANES participants were eligible to complete an interview with a trained survey interviewer involving dietary Supplements and prescription medications. The questions related to prescription medications cover the use of prescription medications during a one-month period prior to the survey date. During the interview, generic names and codes of prescriptions taken by the participant during the previous month were recorded. We linked these codes to statin medications (Atorvastatin, Atorvast, Fluvastatin, Lovastatin, Pitavastatin, Pravastatin, Rosuvastatin, and Simvastatin) to determine whether participants were taking a statin. Data from participants included in the current study indicate that `r statins` of US adults ages 40-79 years used a statin from 2013 to 2018. In case the reviewer would also like to assess the unweighted count, a total of `r statins_unweighted` participants had at least one prescription that was a statin in the current study. Statin usage clearly impacts CVD risk, but only plays a role in the Pooled Cohort risk equations for 10-year ASCVD risk if a statin user responds 'yes' to the question 'Are you receiving treatment for high blood pressure?' due to their statin use. Since we have already partitioned the sample based on self-reported usage of medication to lower blood pressure, we have not included additional data on statin use in the revised manuscript.

<br>

__Comment 3__: The current US definition and staging of hypertension are different than in all other countries. This issue should be addressed in the discussion.

__Response__: We think this is a good topic to include in the Discussion and have included an additional paragraph (see page 16) to address it: "The 2017 ACC/AHA BP guideline's definition of hypertension and recommendations for initiating antihypertensive medication differ from other guidelines published from 2015-2020. For example, the 2018 European Society of Cardiology (ESC) and European Society of Hypertension (ESH) BP guideline recommends considering initiation of antihypertensive medication for adults at very high risk of CVD with untreated SBP between 130 and 139 mm Hg or untreated DBP between 85 and 89 mm Hg. Adults with predicted 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations, severe CKD (eGFR < 30 mL/min/1.73 m^2^), or diabetes with target organ damage are included in the very high CVD risk group. The current study found that many US adults with CKD (eGFR <60 mL/min/1.73 m^2^ or albuminuria) or diabetes did not have high ASCVD risk, defined as clinical CVD or 10-year ASCVD risk ≥ 10% according to the Pooled Cohort Risk equations. Future studies may assess generalization of the current study's findings to the ESC/ESH guideline by estimating the proportion of European adults with diabetes and target organ damage or severe CKD that have clinical CVD or 10-year CVD mortality risk ≥ 10% according to the Systematic Coronary Risk Evaluation equations."

### 2021-06-24 doc/ACCAHA_BP_groups.Rmd
adding LDL

__Word count (including references, but not tables and legends)__: 3837

@@

__number of figures__: 5 (2 main figures, 3, supplemental figues)

@@

Analyses were conducted for the overall population and among `r make_revision("non-exclusive subgroups of")` participants with diabetes, CKD, ≥ 65 years of age, and with any of these three characteristics. Participant characteristics were summarized as mean with its standard error for continuous variables and percentage for categorical variables. The percentage of US adults in each of the five categories based on BP and antihypertensive medication use was computed. `r make_revision("The percentage of US adults with stage 1 hypertension incorrectly assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed.")` The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the percentage of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use. To assess the extent to which participants with a 10-year predicted ASCVD risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted ASCVD risk. The probability of having high ASCVD risk was estimated for each year of age from 40 to 79 years using logistic regression. Analyses of participant characteristics, the distribution of 10-year predicted ASCVD risk, and the probability of having high ASCVD risk were repeated among participants with stage 1 hypertension.

@@

Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had diabetes, CKD, or ≥ 65 years of age (`r refer_to('tab_characteristics')`). The estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`). `r make_revision(paste0("Among those without high ASCVD risk and with stage 1 hypertension, ", table_value(perc_assumed_highrisk), "% were assumed to have high ASCVD risk by the ACC/AHA BP guideline."))` Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.

@@

>>>>

__Word count (including references, but not tables and legends)__: 4117

@@

__number of figures__: 5 (2 main figures, 3, supplemental figures)

@@

Analyses were conducted for the overall population and among `r make_revision("non-exclusive subgroups of")` participants with diabetes, CKD, ≥ 65 years of age, and with any of these three characteristics. Participant characteristics were summarized as mean with its standard error for continuous variables and percentage for categorical variables. The percentage of US adults in each of the five categories based on BP and antihypertensive medication use was computed. `r make_revision("The percentage of US adults with stage 1 hypertension and 10-year predicted ASCVD risk < 10% assumed to have high ASCVD risk by the ACC/AHA guideline due to diabetes, CKD, or age was also computed.")` The 25^th^, 50^th^, and 75^th^ percentile of 10-year predicted ASCVD risk and the percentage of participants with high ASCVD risk were estimated for the overall population and within each of the five categories based on BP and antihypertensive medication use. To assess the extent to which participants with a 10-year predicted ASCVD risk < 10% were close to the 10% threshold, we estimated the distribution of 10-year predicted ASCVD risk. The probability of having high ASCVD risk was estimated for each year of age from 40 to 79 years using logistic regression. Analyses of participant characteristics, the distribution of 10-year predicted ASCVD risk, and the probability of having high ASCVD risk were repeated among participants with stage 1 hypertension.

@@

Among US adults aged 40 to 79 years in `r min(exams)`-`r max(exams)+1`, the estimated prevalence (95% confidence interval [CI]) of diabetes and CKD was `r inline$prevDiabetesOverall` and `r inline$prevCkdOverall`, respectively, `r inline$prevAge65Overall` were estimated to be ≥ 65 years of age, and `r inline$prevAnyOverall` had diabetes, CKD, or ≥ 65 years of age (`r refer_to('tab_characteristics')`). The estimated prevalence (95% CI) of stage 1 hypertension was `r inline$prevS1hOverall` overall and `r inline$prevS1hDiabetes`, `r inline$prevS1hCkd`, `r inline$prevS1hAge65`, and `r inline$prevS1hAny` among those with diabetes, CKD, age ≥ 65 years, and at least one of these conditions, respectively (`r refer_to('tab_bpdist')`). `r make_revision(paste0("Overall, ", table_value(perc_assumed_highrisk), "% of those with stage 1 hypertension and without high ASCVD risk were assumed to have high ASCVD risk by the ACC/AHA BP guideline."))` Characteristics of US adults 40 to 79 years of age with stage 1 hypertension, overall and for subgroups defined by diabetes, CKD and age ≥ 65 years, are presented in Table S1.

@@

`r rp$supplement.table$caption[2]` 
`r fp_par(line_spacing = 1)`
`r rp$supplement.table$object[[2]]`
